---
title: "Documentation 1 - R-Codes"
author: |
  |  Mattia Rossi, PhD Student <mattia.rossi@eurac.edu <br>
  |  EURAC Reserach, Institute for Earth Observation
  |  Free University of Bolzano, Faculty of Science and Technology
output:
  html_document:
    number_sections: yes
    theme: lumen
    toc: yes
    toc_float:
      smooth_scroll: no
  pdf_document:
    toc: yes
    keep_tex: yes
---

# General Information

This R Markdown File serves as documentation of the Data produced within the PhD Thesis of Mattia Rossi starting in 11/16 and ending on 11/19.<br>
The Scripts produced are stored in different Sections for each of the handled dataset in the thesis. These are:

* Ground sampled Data (Fieldwork)
    + 6 different sites in South Tyrol
    + Gradients in spatial location, exposition, altitude and site management
<br>
* Ground sampled Data (Fixed Station)
    + Aquired within the [MONALISA Framework](http://monalisasos.eurac.edu/sos/)
    + 10 Station with constant collection of vegetation metrics beginning in early 2015
    + NDVI, PRI, Soil TEmperature, Soil Water content measurement
    + St

Test

# Province Data

This Section describes the access to meteorological Data by the Province of South Tyrol. The Data is hosted on the [Open Access of South Tyrol](http://daten.buergernetz.bz.it/) and openly available. These are accessed via R interrogating a [central API](http://dati.retecivica.bz.it/dataset/misure-meteo-e-idrografiche/resource/54aaa7f3-5bd2-4fe5-a242-75dd15c21c49). <br>
The following sections provide an overview on the base functions and workflows established for evaluating the Data from the Stations of the Province.


## Repository

A [Gitlab Repository](https://gitlab.inf.unibz.it/SOS/ProvinceST_R_Access) with central functionalities to access, view and download the data has been established and can be accessed for registered members by typing. For now the functions are divided in different scripts and not yet written as a R-Package. Therefore the Functions are imported directly from the R-Script stored locally.


```{r,message=FALSE,warning=FALSE}

path<-"C:/Users/MRossi/Documents/07_Codes/ProvinceST_R_Access/R/"
source(paste0(path,"DependingFunctions.R"))
source(paste0(path,"ProvinceST_StationDownload.R"))
```


## Data Overview

This repository hosts different functions to access and handle the data provided by the meteorological service of South Tyrol. Once the repository is downloaded the downloaded core codes have to be in
As soon as this R-Script is loaded into the Workspace the functions are fully accessable. These contain scripts to simply access the database. <br>
The station network of the meteorological service of South Tyrol is very widespread. Below central information about the station networ are provided. <br>

The station can be interrogated as follows: <br>
```{r}

stations<-.STMeteo_getStation(as="table")
stations
```

The Properties available are: <br>
```{r}

stations<-.STMeteo_getallSCODE()
stations[,1:3]
```

Additionally the Available Stations can be plotted via the Leaflet packages. Every single point on the map indicates one Station of the meteoroglical service.

```{r,eval=FALSE}

ST<-readOGR("C:/Users/MRossi/Documents/03_Data/Shapes/00_General","SouthTyrol")
stations_spatial<-.STMeteo_getStation(as="spatial")
m1<-.STMeteo_plotStation(stations_spatial)
m1<-m1 %>% addPolygons(data=ST,fill=NA,col="black")

```


